---
title: "examples"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(BEASTHandleR)
library(ggplot2)
```

This is a simple script to present the functionality of some of the functions.
```{r}
# Locate the log file
log <- system.file("extdata", "RHDV2.log", package = "BEASTHandleR")

# Age of most recent sample
maxRHDV2 <- 2017.863

# Read log efficiently with data.table
logRHDV2 <- read.log(log, burnin = 0.1)
```

```{r}
# Generate a plot where the demes are overimposed
# use 'step' because changeTimes are fixed
RHDV2_R0_p <- make.BDMMbyDeme.skyplot(log = logRHDV2, type = "step", maxAge = maxRHDV2)
RHDV2_R0_p
```
This is may be useful when wanting to compare different demes, but in this case they are so similar that it gets very confusing. Since the plot is a ggplot object is straightfoward to separate:
```{r}
RHDV2_R0_p + facet_grid(Deme~.)

```
I find that sometimes a good way to present differences in the same deme is to have one violin plot for each epoch, like so: 
```{r}
viol <- make.BDMMbyDeme.violin(logRHDV2, par="R0", keepScale=FALSE) 
viol
```
Sometimes is useful to get rid of long tails to make differences more visible:
```{r}
viol + ylim(c(0,4))
```
